Analyzing Factors Affecting Pakistan Cricket Team's Performance (1952-2024)

### 2024-12-11 paper/paper.qmd
Update paper.qmd

---
title: "Analyzing Factors Affecting Pakistan Cricket Team's Performance (1952-2024)"
subtitle: "Opponent and Coin Tossplay Play Key Role in Deciding Outcome"
author: 
  - Muhammad Abdullah Motasim
thanks: "Code and data are available at: [https://github.com/abdullah-motasim/Analyzing-Pakistans-Cricket-Data](https://github.com/abdullah-motasim/Analyzing-Pakistans-Cricket-Data)."
date: today
date-format: long
abstract: "This paper analyzes Pakistan's cricket performance from 2002 to 2024, using a linear regression model to examine factors influencing match outcomes. We find that opponent strength and toss outcomes are significant predictors of Pakistan's success, highlighting both internal team dynamics and external variables. These findings provide information for coaches, analysts, and administrators, offering strategies to improve performance under varying conditions. Ultimately, our analysis contributes to a deeper understanding of the factors that drive Pakistan’s cricket success, with implications for teams worldwide."
format: pdf
number-sections: true
bibliography: references.bib
table-of-contents: true
toc-depth: 2
editor: 
  markdown: 
    wrap: 72
---

@@

This model provides a useful framework for estimating Pakistan's
likelihood of winning a match based on key factors. By using a Bayesian
Logistic Regression approach, the model incorporates uncertainty in the
estimates, offers a clear interpretation of the effects of each
predictor, and is flexible enough to adapt to new data as it becomes
available. However, it should be acknowledged that there are limitations
regarding omitted variables and potential model assumptions that could
be addressed in future iterations.

>>>>

---
title: "Analyzing Factors Affecting Pakistan Cricket Team's Performance (1952-2024)"
subtitle: "Opponent and Coin Tossplay Play Key Role in Deciding Outcome"
author: 
  - Muhammad Abdullah Motasim
thanks: "Code and data are available at: [https://github.com/abdullah-motasim/Analyzing-Pakistans-Cricket-Data](https://github.com/abdullah-motasim/Analyzing-Pakistans-Cricket-Data)."
date: today
date-format: long
abstract: "This paper analyzes Pakistan's cricket performance from 1952 to 2024, using a linear regression model to examine factors influencing match outcomes. We find that opponent strength and toss outcomes are significant predictors of Pakistan's success, highlighting both internal team dynamics and external variables. These findings provide information for coaches, analysts, and administrators, offering strategies to improve performance under varying conditions. Ultimately, our analysis contributes to a deeper understanding of the factors that drive Pakistan’s cricket success, with implications for teams worldwide."
format: pdf
number-sections: true
bibliography: references.bib
table-of-contents: true
toc-depth: 2
editor: 
  markdown: 
    wrap: 72
---

@@

This model provides a useful framework for estimating Pakistan's
likelihood of winning a match based on key factors. By using a Bayesian
Logistic Regression approach, the model incorporates uncertainty in the
estimates, giving us a clear interpretation of the effects of each
predictor, and is flexible enough to adapt to new data as it becomes
available. However, it should be acknowledged that there are limitations
regarding omitted variables and potential model assumptions that could
be addressed in future iterations.
